---
title: "Junca_E5"
author: "Carolina Junca"
date: "3/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev = "png",  dpi = 100)

```

## Exercises
Save all the graphics in the folder “results” in png format with a resolution of 100 dpi.

### Exercise 1
For the data InsectSpray, make a table for the number of insects for each spray with the mean, median and standard error.
```{r}
#Table with general mean, median and standard error
# x <- (InsectSprays$count)
# mn <- mean(x)
# s_e <- sd(x)/sqrt(length(x))
# mdn <- median(x)
# df <- data.frame(InsectSprays$spray,x,mn,s_e,mdn)

for (i in (InsectSprays$count ~ InsectSprays$spray)){
  print (i)
  mn <- c(mn, mean(i))
  s_e <- c(s_e, sd(i)/sqrt(length(i)))
  mdn <- c(mdn,median(i))
  df <- data.frame(mn,s_e,mdn)
}
plot(InsectSprays$count ~ InsectSprays$spray)
# mn <- numeric()
# s_e <- numeric()
# mdn <- numeric()
# for (i in levels (as.factor(InsectSprays$spray))){
#   SS <- subset.data.frame(InsectSprays, subset = InsectSprays$spray == i)
#   x <- (SS$count)
#   mn <- c(mn, mean(x))
#   s_e <- c(s_e, sd(x)/sqrt(length(x)))
#   mdn <- c(mdn,median(x))
    # df <- data.frame(x,mn,s_e,mdn)
    # Df <- c(df, )
# }
#df <- data.frame(x,mn,s_e,mdn)
```
###Exercise 2
Print a plot to see the differences of counts between sprays. Include a caption explaining the figure. Which type of plot is the one you choose and why?
```{r}
plot(df)
my.table <- trees[1:5, ]

knitr::kable(my.table, caption = “Table 1. Five first rows of the trees dataframe from base R.”)
## Including Plots

You can also embed plots, for example:
```{r}
knitr::

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
